---
title: "Tests on running inference on the mediapipe .tflite obd model inference tool web for l3f"
author: "Botond Ortutay"
output: pdf_document
---

### Situation overview

This document is a summary of tests run on the mediapipe .tflite obd model inference web tool I built for the l3f project. It aims to confirm the web tool is reliable & usable across multiple hardware options without crashing & misbehavior. This is a summary of multiple tests

### Setup

#### Tests  

For every test we record the following environment variables:

 - device
 - OS
 - browser + version
 - camera
 - target sampling rate
 - model
 - delegate
 - score treshold
 - goal of test
 - duration of test
 - special notes on env

, where

 - **browser + version** is (`index.html` -> Environment -> Browser) rendering
 - **target sampling rate** is the `fps` parameter given to `startCameraInferenceLoop()` when called from within `handleStartCamera()` in `src/main.js`
 - **model** is: `DIRNAME` where `data_and_training/models/DIRNAME/model.tflite` is identical to `browser_app/public/models/model.tflite`; Test: `cmp browser_app/public/models/model.tflite data_and_training/models/DIRNAME/model.tflite` -> silent exit, no `browser_app/public/models/model.tflite data_and_training/models/DIRNAME/model.tflite differ: byte xx, line y` type output.
 - **delegate** is the `delegate` parameter given to `ObjectDetector.createFromOptions` in model loading/compilation section of `try` block of `startApplication()` function in `src/main.js`
 - **score treshold** is the `scoreThreshold` parameter given to `ObjectDetector.createFromOptions` in model loading/compilation section of `try` block of `startApplication()` function in `src/main.js`

and we collect

 - csv formatted measurements (camera fpc, sampling fps, inference fps, inference latency) & appropriate visualisations
 - UI beahvior observations
 - browser command line prints of note
 - other notes

, where

**browser command line prints of note** means we ignore per-detection/per-measurement prints, but note any execution time errors.

#### Technical  

Render this document by running `Rscript -e "rmarkdown::render('reporting.Rmd')"` From `browser_app/measurements/`

Libraries:

```{r}
# For data manipulation
suppressPackageStartupMessages(library(dplyr)) # <- Don't print warning on import
library(tidyr)

# For plotting & rendering
library(ggplot2)
library(scales)
```

Diagram drawing function (edited for Rmd use from `data_and_training/devtools/fpsdiagram.R`):

```{r}
fpsdiagram <- function(input_filename) {

  if (!file.exists(input_filename)) {
    stop(
      paste0("Error: File '", input_filename, "' not found."),
      call. = FALSE
    )
  }

  df <- read.csv(input_filename, stringsAsFactors = FALSE)

  df$Timestamp <- as.POSIXct(
    df$Timestamp,
    format = "%Y-%m-%dT%H:%M:%OSZ",
    tz = "UTC"
  )

  df_long <- df %>%
    pivot_longer(
      cols = c(Camera_FPS, Sampling_FPS, Inference_FPS),
      names_to = "Metric",
      values_to = "FPS"
    )

  p <- ggplot(
    df_long,
    aes(x = Timestamp, y = FPS, color = Metric)
  ) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    scale_x_datetime(labels = date_format("%H:%M:%S")) +
    labs(
      title = "Performance Monitoring Metrics",
      subtitle = paste("File:", input_filename),
      x = "Timestamp (UTC)",
      y = "FPS",
      color = "Metric"
    ) +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      axis.text.x = element_text(angle = 45, hjust = 1)
    )

  print(p)
}
```

### Test series 1: Finding the optimal sampling rate

#### Test 1.1 starting from a low baseline

##### Environment

 - device: Self built PC (AMD Ryzen 7 3700X, 16GB RAM, Nvidia Geforce GTX 1660 Super)
 - OS: Fedora Linux 42 (Workstation Edition)
 - browser + version: Mozilla/5.0 (X11; Linux x86_64; rv:143.0) Gecko/20100101 Firefox/143.0
 - camera: Logitech, Inc. C920 HD Pro Webcam
 - target sampling rate: 5
 - model: `ssd_plus_mobilenet_v2_l3f_20260807_225848`
 - delegate: CPU
 - score treshold: 0.35
 - goal of test: baseline establishment
 - duration of test: ~1 min
 - special notes on env: -

##### Results  

```{r}
fpsdiagram("fps_sr5_20260921_212518.csv")
```

No record of browser command line prints.  

Notes: `Inference_FPS` matches `Sampling_FPS`, significantly below `Camera_FPS`, can raise.  

#### Test 1.2 raising to 10 fps sampling

##### Environment

 - device: Self built PC (AMD Ryzen 7 3700X, 16GB RAM, Nvidia Geforce GTX 1660 Super)
 - OS: Fedora Linux 42 (Workstation Edition)
 - browser + version: Mozilla/5.0 (X11; Linux x86_64; rv:143.0) Gecko/20100101 Firefox/143.0
 - camera: Logitech, Inc. C920 HD Pro Webcam
 - target sampling rate: 10
 - model: `ssd_plus_mobilenet_v2_l3f_20260807_225848`
 - delegate: CPU
 - score treshold: 0.35
 - goal of test: baseline establichment
 - duration of test: ~1 min
 - special notes on env: -

##### Results  

```{r}
fpsdiagram("fps_sr10_20260921_214321.csv")
```

No record of browser command line prints.  

Notes: `Inference_FPS` matches `Sampling_FPS`, still below `Camera_FPS`, can raise.

#### Test 1.3 reaching camera fps

##### Environment

 - device: Self built PC (AMD Ryzen 7 3700X, 16GB RAM, Nvidia Geforce GTX 1660 Super)
 - OS: Fedora Linux 42 (Workstation Edition)
 - browser + version: Mozilla/5.0 (X11; Linux x86_64; rv:143.0) Gecko/20100101 Firefox/143.0
 - camera: Logitech, Inc. C920 HD Pro Webcam
 - target sampling rate: 15
 - model: `ssd_plus_mobilenet_v2_l3f_20260807_225848`
 - delegate: CPU
 - score treshold: 0.35
 - goal of test: baseline establishment
 - duration of test: ~1 min
 - special notes on env: -

##### Results  

```{r}
fpsdiagram("fps_sr15_20260921_214710.csv")
```

No record of browser command line prints.  

Notes: `Inference_FPS` & `Sampling_FPS` now occasionally abouve `Camera_FPS`, will lower.  

#### Test 1.4 achieving stability

##### Environment

 - device: Self built PC (AMD Ryzen 7 3700X, 16GB RAM, Nvidia Geforce GTX 1660 Super)
 - OS: Fedora Linux 42 (Workstation Edition)
 - browser + version: Mozilla/5.0 (X11; Linux x86_64; rv:143.0) Gecko/20100101 Firefox/143.0
 - camera: Logitech, Inc. C920 HD Pro Webcam
 - target sampling rate: 14
 - model: `ssd_plus_mobilenet_v2_l3f_20260807_225848`
 - delegate: CPU
 - score treshold: 0.35
 - goal of test: baseline establishment
 - duration of test: ~1 min
 - special notes on env: -

##### Results  

```{r}
fpsdiagram("fps_sr14_20260921_215016.csv")
```

No record of browser command line prints.  

Notes: `Inference_FPS` & `Sampling_FPS` now stable below `Camera_FPS`, not surpassing it. NOTE: `Latency_MS` (how long it actually takes to complete an inference) ranges from 46 to 49. It is still realistic to raise it. We're bottlenecked by `Camera_FPS` on this hardware.  

### Test series 2: On different devices

#### Test 2.1 on an old laptop (Thinkpad T420)

##### Environment

 - device: Thinkpad T420 (Intel Core i5-2520M, 12GB RAM, no dedicated GPU)
 - OS: Lubuntu 25.04
 - browser + version: Mozilla/5.0 (X11; Linux x86_64; rv:150.0) Gecko/20100101 Firefox/150.0
 - camera: Integrated Camera
 - target sampling rate: 14
 - model: `ssd_plus_mobilenet_v2_l3f_20260807_225848`
 - delegate: CPU
 - score treshold: 0.35
 - goal of test: baseline on laptop
 - duration of test: ~1 min
 - special notes on env: -

##### Results  

```{r}
fpsdiagram("fps_t420_20260922_194937.csv")
```

Nothing noteworthy in browser commandline. Only `[Webcam inference]` and `[Webcam measurements]` prints.  

Notes: `Camera_FPS` ranges from below 8 to just around 10. `Sampling_FPS` & `Inferece_FPS` hovers around 10. `Latency_MS` ranges from 97 to 103. The limiting factor with this setup is still `Camera_FPS`, but it's noticably lower than on other computer. Will set sampling rate to 7 to achieve stability.

#### Test 2.2 T420, lowered sample rate

##### Environment

 - device: Thinkpad T420 (Intel Core i5-2520M, 12GB RAM, no dedicated GPU)
 - OS: Lubuntu 25.04
 - browser + version: Mozilla/5.0 (X11; Linux x86_64; rv:150.0) Gecko/20100101 Firefox/150.0
 - camera: Integrated Camera
 - target sampling rate: 7
 - model: `ssd_plus_mobilenet_v2_l3f_20260807_225848`
 - delegate: CPU
 - score treshold: 0.35
 - goal of test: baseline on laptop
 - duration of test: ~1 min
 - special notes on env: -

##### Results  

```{r}
fpsdiagram("fps_t420_sr7_20260922_204808.csv")
```

Nothing noteworthy in browser commandline. Only `[Webcam inference]` and `[Webcam measurements]` prints.  

Notes: `Camera_FPS` suddenly jumped to around 15. So the limiting factor probably wasn't the `Camera_FPS` but the inference. Inferences now range from 98 to 114, which is unusual. Trying to reach a slightly better baseline at 8 fps.

#### Test 2.3 T420, attempting to reach a better baseline at 8fps

##### Environment

 - device: Thinkpad T420 (Intel Core i5-2520M, 12GB RAM, no dedicated GPU)
 - OS: Lubuntu 25.04
 - browser + version: Mozilla/5.0 (X11; Linux x86_64; rv:150.0) Gecko/20100101 Firefox/150.0
 - camera: Integrated Camera
 - target sampling rate: 8
 - model: `ssd_plus_mobilenet_v2_l3f_20260807_225848`
 - delegate: CPU
 - score treshold: 0.35
 - goal of test: baseline on laptop
 - duration of test: ~1 min
 - special notes on env: -

##### Results  

```{r}
fpsdiagram("fps_t420_sr8_20260922_213934.csv")
```

Nothing noteworthy in browser commandline. Only `[Webcam inference]` and `[Webcam measurements]` prints.  

Notes: `Camera_FPS` behaves in a weird & unexpected manner; Spikes reach over 20, pits are at inference/sampling fps. Rates. Inference latency range is huge (96 to 115), but a huge portion of it is around 100-105, with only a few exceptions at the tails. The results for this test show that it's better to keep using 7 fps sampling on laptop still. So that is my laptop baseline from now on. Next I will try whether or not changing from the integrated camera to an external webcam has any effect on anything. The hypothesis is no.

#### Test 2.4 T420, changing the camera

##### Environment

 - device: Thinkpad T420 (Intel Core i5-2520M, 12GB RAM, no dedicated GPU)
 - OS: Lubuntu 25.04
 - browser + version: Mozilla/5.0 (X11; Linux x86_64; rv:150.0) Gecko/20100101 Firefox/150.0
 - camera: Logitech, Inc. C920 HD Pro Webcam
 - target sampling rate: 7
 - model: `ssd_plus_mobilenet_v2_l3f_20260807_225848`
 - delegate: CPU
 - score treshold: 0.35
 - goal of test: seeing the affect of changing the camera
 - duration of test: ~1 min
 - special notes on env: -

##### Results  

```{r}
fpsdiagram("fps_t420_logitech_base.csv")
```

Nothing noteworthy in browser commandline. Only `[Webcam inference]` and `[Webcam measurements]` prints.  

Notes: Contrary to my expectations, there is a wild jump in `Camera_FPS`. All values are now over 15 fps, meaning that sampling rate can be increased. `Latency_MS` ranges from 101 to 112. This prompts two new investigations: sr8 and sr14 on t420+logitech
